The development of infants' responses to mispronunciations: A Meta-Analysis

### 2019-06-03 VonHolzenBergmann_MPMetaAnalysis.Rmd
first draft of monster paper, updated random effects structure

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the google scholar search engine to search for papers citing the original @Swingley2000 publication. This search was conducted on 22 September, 2017 and yielded 288 results. We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (n = *`r length(unique(descriptive_dat$short_cite))`*) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table 1 provides an overview of all papers included in the present meta-analysis.

@@

@@

A detailed explanation for moderating factors 3-8 can be found in their respective sections in the Results. We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials. When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  [e.g., consonant versus vowel mispronunciations; @Mani2007].  The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section). We will call each row a record; in total there were `r nrow(descriptive_dat)` records in our data.

@@

rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
# Publication bias can become visible in funnel plot asymmetry. 
# Metafor comes with several options to check this, I chose ranktest and regtest
# correct object identification
rmac <- ranktest(rma_correct)
#rmac

@@

rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ same_infant_calc | short_cite)

@@

# rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)

@@

#rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ same_infant_calc | short_cite)

@@

#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ same_infant_calc | short_cite)

@@

rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ same_infant_calc | short_cite)

@@

rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ same_infant_calc | short_cite)

@@

rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = ~ same_infant_calc | short_cite)

@@

dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, df$n_feature)

@@

# overall object recognition
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~n_feature, data = dat.f, random = ~ same_infant_calc | short_cite)

@@

dat.f <- subset(dat, n_feature != "2_3" & n_feature != "1_2" & n_feature != "1_2_3")
dat.f$n_feature <- factor(dat.f$n_feature, levels = c("0", "1", "2", "3"))
dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, df$n_feature)

@@

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat, random = ~ same_infant_calc | short_cite)

@@

# age moderator
rma_Distractor_age <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition*age.C, data = dat, random = ~ same_infant_calc | short_cite)

@@

@@

rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = ~ same_infant_calc | short_cite)

@@

@@

rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ same_infant_calc | short_cite)

@@

@@

To understand the relationship between mispronunciation position and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation position and condition as moderators. The moderator test was significant, `r mod_test(rma_LocationCondition)`. For the interaction between condition and mispronunciation position, the estimate was small but significant ($\beta$ `r full_estimate(sum_eff)`. As can be seen in Figure \@ref(fig:PlotMispPosit)a, mispronunciation sensitivity decreased linearly as the position of the mispronunciation moved later in the word, with sensitivity greatest for onset mispronunciations and smallest for coda mispronunciations.

To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator. The moderator test was significant, `r mod_test(rma_Misp_Posit_age_MS)`. The estimate for the three-way interaction between age, condition, and mispronunciation position was not significant ($\beta$ `r full_estimate(sum_eff_age_medial)`. As can be seen in Figure \@ref(fig:PlotMispPosit)b, mispronunciation sensitivity but stays relatively stable for onset and medial mispronunciaitons. For mispronunciations on the coda position it appears that mispronunciation sensitivity increases with age, but this is likely underpowered and therefore not detectable by our meta-analysis.

Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test. The results were significant, *p* `r psig(fish.test$p.value)`. Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations. An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions (Marslen-Wilson & Zwitserlood, 1989), and therefore easier to detect. For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity. However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations. We return to this issue in the General Discussion.

@@

sum_eff_tc <- coef(summary(rma_TypeFeaturesMP_Condition))[11,]
sum_eff2_tv <- coef(summary(rma_TypeFeaturesMP_Condition))[12,]

@@

We further included an exploratory analysis of the relationship between infant age and the impact of tone mispronunciations in comparison to consonant and vowel mispronunciations. We included mispronunciation type, condition (correct pronunciation, mispronunciation) as well as age as additional moderators. The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_ConditionT)`, but the interactions between condition, age, and both consonant ($\beta$ = `r full_estimate(sum_eff_tc$estimate)`) and vowel ($\beta$ = `r full_estimate(sum_eff_tv$estimate)`) mispronunciations were not significant. Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.

@@

#### Onset time after target naming

@@

The results of the moderator analysis reflect several experimental findings. Although words differ from one another on many acoustic dimensions, changes in phonemes, as measured by phonological features, signal changes in meaning. Several studies have found that infants show graded sensitivity to both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes. This was captured in our meta-analysis, which also showed that sensitivity to mispronunciations increased linearly with the number of phonological features changed. For each increase in number of phonological features changed, the effect size estimate for looks to the target decreases by `r r2(linear_feature)`. Yet, this graded sensitivity appears to be stable across infant ages, although our analysis was likely underpowered. At least one study suggests that this graded sensitivity develops with age, but this was the only study to examine more than one age (Mani & Plunkett, 2011). All other studies only test one age (Tamasi, White & Morgan, 2008; Bernier & White, 2017). With more studies investigating graded sensitivity at multiple ages in infancy, we would achieve a better estimate of whether this is a stable or developing ability.

Although some theories place greater importance on onset position for word recognition and decreasing importance for phonemes in subsequent positions (COHORT), other theories suggest that lexical access can still recover (TRACE). Is there any experimental evidence? That swingly study? Our results show that infants are more sensitive to mispronunciations earlier in the word. Since few studies actually compare this, this is nice evidence to have and should hopefully spure more studied. Again, we find no influence of development.

in general, these are the things that support what has been found in the literature or theories

These things were not supported

** Position of mispronunciation **

  + effect size estimate later position in words significantly decreases
  + no effect of age
  + Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test. The results were significant, *p* `r psig(fish.test$p.value)`. Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations. An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions (Marslen-Wilson & Zwitserlood, 1989), and therefore easier to detect. For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity. However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations. We return to this issue in the General Discussion.

 The influence of distractor overlap also depends on the *position of mispronunciation* in the word, which can be at word onset, medial, or final positions. Models of spoken word processing place more or less importance on the position of a phoneme in a word. The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.  In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.

  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth. In early language acquisition, infants typically know more consonant compared to vowel onset words. When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.

** Phonological overlap between target and distractor **

  + mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap
  + this is rather the opposite of what one would expect, right?
  + [Katie: Yeah! Its really strange, so the time course analysis suggestion of yours is a very good one!]
  + Maybe it would be useful to have time course analyses to address this issue further
  + mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap
  + The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`. Older infants were more likely to be tested in experimental conditions where target and distractor images overlapped on their onset phoneme, while younger infants were more likely to be tested with target and distractor images that did not control for overlap. A distractor image that overlaps in the onset phoneme with the target image is considered a more challenging task to the infant, as infants must pay attention to the mispronounced phoneme and can not use the differing onsets between target and distractor images to differentiate (Fernald, Swingley, & Pinto, 2001). It therefore appears that older infants were given a more challenging task than younger infants. This may explain why infants in the onset overlap condition, a harder task, have a greater effect size estimate for mispronunciation sensitivity than those in the no overlap condition, which is a comparably easier task. We return to this issue in the General Discussion.

  Furthermore, when presenting infants with a familiar distractor image, some studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001). Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.

** Type of mispronunciation **

  + Overall, no difference between consonants and vowels 
  + Consonant mispronunciation sensitivity stays the same with age
  + Vowel mispronunciation sensitivity increases with age
  + mispronunciation sensitivity for consonants similar for Germanic and Romance languages
  + Mispronunciation sensitivity for vowels greater for Germanic compared to Romance languages
  + For Germanic infants, sensitivity to consonant and vowel mispronunciations did not change with age. 
  + For Romance infants, sensitivity to mispronunciations decreases for consonants and increases for vowels with age
  + exploratory analyses with tone mispronunciations suggest no great difference in sensitivity when compared to consonant and vowel mispronunciations

** Distractor Familiarity **

  + No difference between familiar and unfamiliar distractors
  + Again, ages not matched very well for the two groups here.

@@

## Limitations

The current meta-analysis aggregated studies designed to investigate mispronunciation sensitivity, but we note that these studies varied in their approach to study our phenomenon of interest. For example, some studies investigated specific questions which required additional manipulations, such as the impact of the number of phonological features changed in the mispronunciations on mispronunciation sensitivity [e.g. @Mani2011; @White2008] or sensitivity to consonant and vowel mispronunciations [@Mani2007; @Mani2010kepstups; @Hojen; @Swingley2016]. The studies in our sample additionally varied in their experimental design, such as whether infants were familiar with the distractor image [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016] or whether the labels for the target and distractor images contained phonological overlap [@Fernald2001a]. Futhermore, the infants included in this meta-analysis had a variety of native languages (English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese) and language backgrounds (monolingual, bilingual, monodialectal, multidialectal). Taken together, these variables have the potential to modulate infant mispronunciation sensitivity, but an investigation of these variables is out of the scope of the current meta-analysis. However, our dataset includes these variables. We hope that future research will be able to better understand the role that these variables play in infants' sensitivity to mispronunciations.

@@

>>>>

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the google scholar search engine to search for papers citing the original @Swingley2000 publication. This search was conducted on 22 September, 2017 and yielded 288 results. We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (*n* = `r length(unique(descriptive_dat$short_cite))`) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table 1 provides an overview of all papers included in the present meta-analysis.

@@

bil_info <- dat %>%
  group_by(group_name_1, short_cite) %>%
  summarize(count = n())

bil_infants <- with(bil_info, count[group_name_1 == "bilingual"])

@@

A detailed explanation for moderating factors 3-8 can be found in their respective sections in the Results [^1]. We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials. When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  [e.g., consonant versus vowel mispronunciations; @Mani2007].  The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section). We will call each row a record; in total there were `r nrow(descriptive_dat)` records in our data.

[^1]: Two papers tested bilingual infants (Ramon-Casas & Bosch, 2010; Ramon-Casas et al., 2011), yielding `r bil_infants` experimental conditions. Due to this small number, we do not investigate the role of multilingualism, but do note that removing these papers from the meta-analysis did not alter the pattern of results.

@@

rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
# Publication bias can become visible in funnel plot asymmetry. 
# Metafor comes with several options to check this, I chose ranktest and regtest
# correct object identification
rmac <- ranktest(rma_correct)
#rmac

@@

rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

# rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

#rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

@@

# overall object recognition
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~n_feature, data = dat.f, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

dat.f <- subset(dat, n_feature != "2_3" & n_feature != "1_2" & n_feature != "1_2_3")
dat.f$n_feature <- factor(dat.f$n_feature, levels = c("0", "1", "2", "3"))
dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, dat.f$n_feature)

@@

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

# age moderator
rma_Distractor_age <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition*age.C, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

# db_ET_MPo_MS = db_ET_MPo_MS %>%
#   filter(mispron_location != "onset")

@@

rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

# db_ET_MPo_MS = db_ET_MPo_MS %>%
#   filter(mispron_location != "onset")
#

@@

rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

 linear_position <- sum_eff$estimate

@@

To understand the relationship between mispronunciation position and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation position and condition as moderators. The moderator test was significant, `r mod_test(rma_LinearLocationCondition)`. For the interaction between condition and mispronunciation position, the estimate was small but significant ($\beta$ `r full_estimate(sum_eff)`. As can be seen in Figure \@ref(fig:PlotMispPosit)a, mispronunciation sensitivity decreased linearly as the position of the mispronunciation moved later in the word, with sensitivity greatest for onset mispronunciations and smallest for coda mispronunciations.

To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator. The moderator test was significant, `r mod_test(rma_LinearLocationCondition_age)`. The estimate for the three-way interaction between age, condition, and mispronunciation position was not significant ($\beta$ `r full_estimate(sum_eff_age)`. As can be seen in Figure \@ref(fig:PlotMispPosit)b, mispronunciation sensitivity but stays relatively stable for onset and medial mispronunciaitons. For mispronunciations on the coda position it appears that mispronunciation sensitivity increases with age, but this is likely underpowered and therefore not detectable by our meta-analysis.

Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test. The results were significant, *p* `r psig(fish.test$p.value)`. Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations. An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions (Marslen-Wilson & Zwitserlood, 1989), and therefore easier to detect. For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity. However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations. It is unlikely that this influenced our developmental trajectory estimate, as the consequence would have been mispronunciation sensitivity that increases with age.

@@

sum_eff_tc <- coef(summary(rma_TypeFeaturesMP_Condition_age))[11,]
sum_eff2_tv <- coef(summary(rma_TypeFeaturesMP_Condition_age))[12,]

@@

We further included an exploratory analysis of the relationship between infant age and the impact of tone mispronunciations in comparison to consonant and vowel mispronunciations. We included mispronunciation type, condition (correct pronunciation, mispronunciation) as well as age as additional moderators. The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_ConditionT)`, but the interactions between condition, age, and both consonant ($\beta$ = `r full_estimate(sum_eff_tc)`) and vowel ($\beta$ = `r full_estimate(sum_eff2_tv)`) mispronunciations were not significant. Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.

@@

#### Offset time after target naming

@@

The results of the moderator analysis reflect several findings that have been found in the literature. Although words differ from one another on many acoustic dimensions, changes in phonemes, as measured by phonological features, signal changes in meaning. Several studies have found that infants show graded sensitivity to both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes. This was captured in our meta-analysis, which also showed that sensitivity to mispronunciations increased linearly with the number of phonological features changed. For each increase in number of phonological features changed, the effect size estimate for looks to the target decreases by `r r2(linear_feature)`. Yet, this graded sensitivity appears to be stable across infant ages, although our analysis was likely underpowered. At least one study suggests that this graded sensitivity develops with age, but this was the only study to examine more than one age (Mani & Plunkett, 2011). All other studies only test one age (Tamasi, White & Morgan, 2008; Bernier & White, 2017). With more studies investigating graded sensitivity at multiple ages in infancy, we would achieve a better estimate of whether this is a stable or developing ability.

Although some theories place greater importance on onset position for word recognition and decreasing importance for phonemes in subsequent positions (i.e. COHORT; Marslen-Wilson & Zwitserlood, 1989), other theories suggest that lexical access can still recover from onset and medial mispronunciations (i.e. TRACE; McClelland & Elman, 1986). Although many studies have examined mispronunciations on multiple positions, only a handful have directly compared sensitivity between different positions. These studies find that position of the mispronunciation does not modulate sensitivity (Swingley, 2009; Zesiger & Jöhr, 2011). This stands in contrast to the findings of our meta-analysis, which showed that for each subsequent position in the word that is changed, from onset to medial and medial to coda, the effect size estimate for looks to the target decreases by `r r2(linear_position)`; infants are more sensitive to changes in the sounds of familiar words when they occur in an earlier position as opposed to a late position.

One potential explanation for the discrepancy between the results of individual studies and that of the current meta-analysis is the difference in how analysis timing is considered depending on the position of the mispronunciation. For example, Swingley (2009) adjusted the offset time from 367 ms for onset mispronunciations to 1133 for coda mispronunciations, to ensure that infants have a similar amount of time to respond to the mispronunciation, regardless of position. In contrast, if an experiment compares different kinds of medial mispronunciations, as in Mani & Plunkett (2011), it is not necessary to adjust offset time because the mispronunciations have a similar onset time. The length of the post-naming analysis window does impact mispronunciation sensitivity, as we discuss below, and by comparing effect sizes for different mispronuciation positions where position timing was not considered, we may have put mispronunciations that occur later in the word (i.e. medial and coda mispronunciations) at a disadvantage relative to onset mispronunciations. These issues can be addressed with the addition of more experiments that directly compare sensitivity to mispronunciations of different positions, as well as the use of analyses that account for differences in timing of sensitivity.

For several moderators, we found no evidence of modulation of mispronunciation sensitivity. For example, sensitivity to mispronunciations was similar for experimental conditions that included either a familiar or an unfamiliar distrator image. Studies that include an unfamiliar, as opposed to familiar distractor image, often argue that the unfamiliar image provides a better referent candidate for mispronunciation than a familiar distractor image, where the name is already known. No studies have directly compared mispronunciation sensitivity for familiar and unfamiliar distractors, but these results suggest that this manipulation alone makes little difference in the design of the experiment. It remains possible that distractor familiarity interacts with other types of manipulations, such as number of phonological features changed, heightening the ability of the experimenter to detect more sublte differences in mispronunciation sensitivity (i.e. White & Morgan, 2008), but our meta-analysis is underpowered to detect these effects.

Despite the proposal that infants should be more sensitive to consonant compared to vowel mispronunciations (Nazzi, Poltrock, & Von Holzen, 2016), we found no difference in sensitivity to consonant and vowel mispronunciations. But, a more nuanced picture was revealed regarding differences between consonant and vowel mispronunciations when further moderators were introduced. Sensitivity to consonant mispronunciations did not change with age and were similar for infants learning Germanic and Romance languages. In contrast, sensitivity to vowel mispronunciations increased with age and was greater for infants learning Germanic languages, although sensitivity to vowel mispronunciations did increase with age for infants learning Romance languages. Sensitivity to vowel mispronunciations is modulated both by development and by native language, whereas sensitivity to consonant mispronunciations is fairly similar across age and native language. This pattern of results support previous experimental evidence that sensitivity to consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language (Nazzi et al., 2016). Additionally, our exploratory analysis of tone mispronunciations revealed no difference in sensitivity in comparison to vowel and consonant mispronunciations, but our ability to detect differences may have been underpowered, as only `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions included tone mispronunciations. We hope that the recent increase in mispronunciation studies investigating infants learning a tone language (e.g. Mandarin Chinese) will soon solve this power issue.

Our meta-analysis revealed the rather surprising result that onset overlap between labels for the target and distractor images lead to greater mispronunciation sensitivity in comparison to target-distractor pairs that shared no phonological overlap. It should be arguably more, not less, difficult to detect a mispronunciation (dag) when the target and distractor overlap in their onset phoneme (dog-duck), because the infant can not use differences in the onset sound between the target and distractor to identify the intended referent. Perhaps including overlap between the target and distractor lead infants to pay more attention to mispronunciations, leading to an increased effect of mispronunciation sensitivity. When we examined the distribution of this manipulation across infant age, however, we found an alternate explanation for this pattern of results. Older children were more likely to recieve the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme. If older children have greater mispronunciation sensitivity in general, then this may have lead to greater mispronunciation sensitivity for overlapping target-distractor pairs, instead of the manipulation itself.

But, our main developmental analysis found a lack of developmental change in mispronunciation sensitivity, suggesting that older children do not have greater mispronunciation sensitivity than younger children. If older children are given a more difficult task than younger children, however, this may dampen any developmental effects. It appears that this may be the case for overlap between target-distractor pairs. Older children were given a more difficult task (target-distractor pairs with onset overlap), which may have lowered the size of their mispronunciation sensitivity effect. Younger children were given an easier task (target-distractor pairs with no overlap), which may have relatively increased the size of their mispronunciation sensitivity effect. As a result, any developmental differences would be erased, hidden by task differences in the experiments that older and younger infants participated in. Further support comes from evidence that sensitivity to mispronunciations when the target-distractor pair overlapped on the onset phoneme increased with age. This pattern of results suggest that when infants are given an equally difficult task, developmental effects may be revealed. This explanation can be confirmed by testing more young infants on overlapping target-distractor pairs.

@@

@@

One unique aspect of this meta-analysis was our examination of
